### 2025-07-02 machine-learning.qmd
20250702 - longitudinal random forest

```{r}
smerf <- LongituRF::MERF(
  X = data_train_qb_matrix %>% as_tibble() %>% dplyr::select(season:att_br.rush) %>% as.matrix(),
  Y = data_train_qb_matrix[,c("fantasyPoints_lag")] %>% as.matrix(),
  Z = data_train_qb_matrix[,c("pacr")] %>% as.matrix(),
  id = data_train_qb_matrix[,c("gsis_id")] %>% as.matrix(),
  time = data_train_qb_matrix[,c("ageCentered20")] %>% as.matrix(),
  ntree = 500,
  sto = "BM")

@@

# Predict on Test Data
predict(
  smerf,
  X = data_test_qb %>% as_tibble() %>% dplyr::select(season:att_br.rush) %>% as.matrix(),
  Z = data_test_qb[,c("pacr")] %>% as.matrix(),
  id = data_test_qb[,c("gsis_id")] %>% as.matrix(),
  time = data_test_qb[,c("ageCentered20")] %>% as.matrix())
```

>>>>

```{r}
smerf <- LongituRF::MERF(
  X = data_train_qb %>% dplyr::select(season:att_br.rush) %>% as.matrix(), # predictors of the fixed effects
  Y = data_train_qb[,c("fantasyPoints_lag")] %>% as.matrix(), # outcome variable
  Z = data_train_qb %>% dplyr::mutate(constant = 1) %>% dplyr::select(constant, passing_yards, passing_tds, passing_interceptions, passing_epa, pacr) %>% as.matrix(), # predictors of the random effects
  id = data_train_qb[,c("gsis_id")] %>% as.matrix(), # player ID (for nesting)
  time = data_train_qb[,c("ageCentered20")] %>% as.matrix(), # time variable
  ntree = 500,
  sto = "BM")

@@

# Predict on Test Data
predict(
  smerf,
  X = data_test_qb %>% dplyr::select(season:att_br.rush) %>% as.matrix(),
  Z = data_train_qb %>% dplyr::mutate(constant = 1) %>% dplyr::select(constant, passing_yards, passing_tds, passing_interceptions, passing_epa, pacr) %>% as.matrix(),
  id = data_test_qb[,c("gsis_id")] %>% as.matrix(),
  time = data_test_qb[,c("ageCentered20")] %>% as.matrix())
```
